---
title: "Chord Diagram"
author: "Deniz, Mileva, Marina"
date: "1/16/2022"
output:
  html_document: default
  pdf_document: default
---

# Import packages

Packages for chord diagrams (circular versions of Sankey). Ranked from best to worst:  
1. chorddiag package (R): This is the only R package for an interactive chord diagram. It's builds on the JavaScript D3 library. (Further information can be found on the GitHub page: https://github.com/mattflor/chorddiag). The only downside is it offers fewer parameters to really fine-tune the appearance of the visualization.  
2. circilize package (R): It only provides a static chord diagram (Explained here: https://www.r-graph-gallery.com/chord-diagram.html), but it allows more parameters to tailor the appearance of the visualization than the chorddiag package.  
3. plotly (Python): Python plotly has functionality to create an interactive chord diagram. The interactive design and features are not as nice as those in the chorddiag package (Documentation: https://plotly.com/python/v3/filled-chord-diagram/).  

Packages for Sankey (non-circular):  
1. networkD3 package (R): This appears to be the primary interactive Sankey diagram package. Further research has to be conducted on the customization provided by the package. See an example here: https://www.data-to-viz.com/graph/sankey.html  
2. Plotly Sankey (R): Further research has to be conducted to determine whether this package or the networkD3 will provide better interactive features.  
3. ggalluvial (R): This appears to provide static Sankey plots.  

Below, we've built an example chord diagram using the chorddiag package and the NCF Alumni data.

```{r cache=TRUE, warning = FALSE, message = FALSE}
library(tidyverse)
library(ggplot2)
library(usethis)
library(devtools)
library(chorddiag)
library(RColorBrewer)
library(magrittr)
```

# Read Data

```{r}
alumns <- read.csv(file="../data/NCAlumn.csv")
#dim(alumns)
colnames(alumns)
head(alumns)
```

# Processing Data
Recoding Academic programs
```{r}
# Recoded factors
aoc.recoded <- alumns$ACADEMIC_PROGRAM_1 %>% fct_lump(prop=0.01)
industry.recoded <- fct_lump(alumns$Industry, n=7)
alumns.recoded <- alumns %>% mutate(Industry = industry.recoded, aoc = aoc.recoded)

# Computation 
data.aoc <- alumns.recoded %>%
    drop_na(aoc, Industry) %>%
    select(aoc, Industry) %>% 
    mutate(Industry=Industry) %>% 
    filter(Industry != "Other")

as.matrix(table(data.aoc))
```

Recoding DIVISION_1
```{r}
# Recoded factors
division_1 <- alumns$DIVISION_1
industry.recoded <- fct_lump(alumns$Industry, n=7)
alumns.recoded <- alumns %>% mutate(Industry = industry.recoded)

# Computation 
data.division <- alumns.recoded %>%
    drop_na(DIVISION_1, Industry) %>%
    select(DIVISION_1, Industry) %>% 
    filter(Industry != 'Other' & Industry != '') %>%
    filter(DIVISION_1 != '') %>%
    mutate(Industry = droplevels(Industry))


as.matrix(table(data.division))
```

```{r}
unique(data.division$Industry)
```

# Chord Diagram
```{r}
dataplot <- as.matrix(table(data.division))

dim(as.matrix(dataplot))
dataplot
```

```{r}
# Number of divisions
num.divisions = length(rownames(dataplot))

# Data/matrix to be plotted
m <- as.matrix(dataplot)
m_transpose<- t(m)

division <- rownames(dataplot)
industry <- colnames(dataplot)
dimnames(m_transpose) <- list(industry = industry,
                    division = division)

# Color scheme
mycols <- brewer.pal(num.divisions ,'Set2')[1:4]

divisionColors <- mycols
industryColors <- rep('grey', length(industry))
colors <- c(industryColors, divisionColors)
```

# Chord Diagram
```{r}
chorddiag(data = m_transpose, 
          type='bipartite',
          groupColors = colors, 
          groupThickness = 0.05,
          groupnamePadding = 10,
          groupnameFontsize = 15,
          showTicks = F, 
          categoryNames = c('Industry', 'Academic Division'), 
          categorynamePadding = 150, 
          categorynameFontsize = 25, 
          fadeLevel = 0.1, 
          tooltipUnit = ' students')
```

